---
title: "Base sample"
output:
  html_document:
    df_print: paged
---


```{r, message=FALSE}
library(readxl)

final <- read_excel("final.xlsx")

final$...1 <- NULL
final$...2 <- NULL
```



```{r,message=FALSE}

library(plm)
library(tidyverse)
library(lfe)
library(lmtest)


```

```{r}
final <- final %>%
  arrange(idem, year) %>%  # Sort by firm and then by year
  group_by(idem) %>%      # Tell dplyr to go within each firm
  mutate(gdp_gro = GDP_pc/(lag(GDP_pc)-1),
         insde_d = ins_effic/(lag(ins_effic)-1),
         tot_d = TOT/(lag(TOT)-1), 
         debt_d = Gov_debt/(lag(Gov_debt)-1),
         redis = Gini_market - Gini_net/Gini_net)


panel.plm.df <- pdata.frame(final, index=c("idem","year"), drop.index=TRUE)
attach(panel.plm.df)
```

Resultados de un modelo con fixed effects y pooling

```{r}
fe_lm <- plm(Gini_net ~ (gdp_gro) + Unempl_rate + Trade + Gov_ex + Secondary_ed ,
                        data = panel.plm.df, 
                        index=c("idem", "year"), model="within", effect = c("individual"))
summary(fe_lm)

yhat <- fe_lm$fitted
plot(final$gdp_gro, final$Gini_net, pch=19, xlab="x1", ylab="y")
abline(lm(final$Gini_net~final$gdp_gro),lwd=3, col="red")

pl_lm <- plm(Gini_net ~ lag(GDP_pc) + lag(Gini_market) + Trade + instdepth + Gov_ex + Secondary_ed ,
                        data = panel.plm.df, 
                        index=c("idem", "year"), model="pooling", effect = c("individual"))

summary(pl_lm)
```

```{r}
library(gplots)
plotmeans(Gini_net ~ idem, main="Heterogeineity across countries", data=final, bars=T, lwd=2)
```


```{r}
pFtest(fe_lm, pl_lm)

# In both cases the null hypothesis is rejected in favor of the alternative that there are significant fixed effects.

```

```{r}
wi_lm <- plm(Gini_net ~ (gdp_gro) + employ_rate +Trade +  Gov_ex + Secondary_ed ,          data = panel.plm.df, 
                        index=c("idem", "year"), model="within", effect = c("twoways"))

summary(wi_lm)

pFtest(fe_lm, wi_lm) 

# There is evidence that time fixed effects should be taken into account.
```


```{r, eval=FALSE}
ra_lm <- plm(Gini_net ~ lag(GDP_pc) + lag(Gini_market) + Trade + instdepth + Gov_ex + Secondary_ed ,
                        data = panel.plm.df, 
                        index=c("idem", "year"), model="random", effect = c("individual"))

summary(ra_lm)
summary(fe_lm)

phtest(fe_lm, ra_lm)

# The null hypothesis cannot be rejected here, hence we should use a FE model.
```

```{r}
lmtest::bptest(Gini_net ~ lag(GDP_pc) + lag(Gini_market) + Trade + instdepth + Gov_ex + Secondary_ed + factor(idem), studentize = F, data = final)

# here is strong evidence for the presense of heteroskedasticity. Hence, the use of robust standard errors is advised.

pbgtest(fe_lm)

# There is strong evidence that the residuals are serially correlated.
```

```{r}
fe_s =coeftest(fe_lm, vcov = (vcovHC(fe_lm, method='arellano',type = "HC1",cluster = "group")))

fe_s
# summary(fe_lm)

# fe_s2 <- lfe::felm(Gini_net ~ lag(GDP_pc) + lag(Gini_market) + Trade + instdepth + Gov_ex + Secondary_ed | idem | 0 | idem, data = final)
# 
# summary(fe_s2)

wi_s =coeftest(wi_lm, vcov = (vcovHC(wi_lm, method='arellano',type = "HC2",cluster = "group")))

wi_s

# ercomp(Gini_net ~ lag(GDP_pc) + lag(Gini_market) + Trade + instdepth + Gov_ex + Secondary_ed, data=final, 
       # method = "nerlove", effect = "twoways")

```

De los resultados anteriores solucionando los problemas de autocorrelación y heteroscedasticidad, vemos que controlando el modelo por tiempo y fixed effects es mejor que sólo con FE.


```{r}
ftime <- plm(Gini_net ~ lag(GDP_pc) + lag(Gini_market) + Trade  + Gov_ex + Secondary_ed  + factor(year),    data = final, index=c("idem","year"), model="within")

summary(ftime)

pFtest(wi_lm, fe_lm)
plmtest(fe_lm, c("time"), type=("bp"))

# If this number is < 0.05 then use time-fixed effects. In this example, no need to use
# time-fixed effects.
```

```{r}
# Testing for cross-sectional dependence

# Evidence of CS dependence and Correlation

pcdtest(fe_lm, test = c("lm"))
pcdtest(fe_lm, test = c("cd"))

pbgtest(fe_lm)

# Presence of heteroskedasticity
bptest(Gini_net ~ lag(GDP_pc) + lag(Gini_market) + Trade + instdepth + Gov_ex + Secondary_ed  + factor(idem), data = final, studentize=F)

coeftest(fe_lm)

fe_so1 <- coeftest(fe_lm, vcovHC(fe_lm, method = "arellano",  type = "HC3"))
fe_so2 <- coeftest(fe_lm, vcovHC(fe_lm, cluster = "group",  type = "HC3"))

wi_so1 <- coeftest(wi_lm, vcovHC(wi_lm, method = "arellano",  type = "HC3"))
wi_so2 <- coeftest(wi_lm, vcovHC(wi_lm, type = "HC3", cluster = "group"))


screenreg(list(fe_so1, fe_so2, wi_so2),
          custom.model.names = c("FE_au", "FE_cd", "Two"))

wi_so2[,1] / diff(range(final$Gini_net, na.rm = TRUE))
```



## LOCAL IMPULSE ESTIMATIONS

```{r}
library(lpirfs)
library(dplyr)
```

```{r}
ln <- final %>%
             dplyr::select(idem, year, Gini_net, GDP_pc, Trade, instdepth, Gov_ex, Secondary_ed)
```

```{r}
results_panel <-  lp_lin_panel(data_set          = ln,
                              # data_sample       = data_sample,
                               endog_data        = "Gini_net",
                               cumul_mult        = TRUE,
                               shock             = "Gov_ex",
                               diff_shock        = T,
                               panel_model       = "within",
                               panel_effect      = "twoways",
                               robust_cov        = "vcovSCC",
                               # c_exog_data       = "Gov_ex",
                               c_fd_exog_data    = colnames(ln)[c(seq(4,8))],
                               l_fd_exog_data    = colnames(ln)[c(seq(4,8))],
                               lags_fd_exog_data = 1,
                               confint           = 1.67,
                               hor               = 10)
```


```{r}
plot_lin_panel <- plot_lin(results_panel)

plot(plot_lin_panel[[1]])

## Government exp shock on Gini_net
```

```{r}
en = ln %>% select(-idem, -year)
en$idem <- NULL

results_lin <- lp_lin(en, 
                           lags_endog_lin = 1,    # Number of lags for endogenous data
                           trend          = 0,    # 0 = no trend, 1 = trend, 2 = trend & trend^2    
                           shock_type     = 1,    # 0 = standard deviation shock, 1 = unit shock
                           confint        = 1.96, # Width of confidence bands: 
                                                  # 1 = 68%, 1.67 = 90%, 1.96 = 95%
                           hor            = 5)   # Number of cores to use. When NULL, the number of cores 
                                                  # is chosen automatically 
```

```{r}
 linear_plots <- plot_lin(results_lin)
  library(ggpubr)
  library(gridExtra)

# Show all plots

lin_plots_all <- sapply(linear_plots[1:6], ggplotGrob)
marrangeGrob(lin_plots_all, nrow = 2, ncol = 3, top = NULL)
```

Efectos locales sobre el Gini-net, solo es una muestra (no definitivo) falta mejorar los parámetros de la estimación.
Y que otras opciones arrojan los resultados... y lo más importante theory!!!

Yo me quedaría con el de arriba que es la de Panel y se puede modificar las variables, solo que tenemos que tener claro que shocks deben afectar al Gini.

Ningún modelo es dinámico, ya va tomando forma.
