- **Hotelbeds is the worlds leading bedbank.**

  The company’s proprietary technology helps providers of travel services distribute their offering to travel sellers globally via an easy-to-use, advanced technology platform that increases reach, revenue and yield for both the provider and the seller.

  Operating under the Hotelbeds brand in the wholesale channel and the Bedsonline brand in the travel agents channel, the company connects over 60,000 travel intermediaries across more than 140 source markets globally with travel providers in over 185 countries representing more than 170,000 hotels, 24,000 transfer routes and 18,000 activities.

  The company is headquartered in Palma de Mallorca, Spain.

  This position sits within our Bedbank unit. **JOB DESCRIPTION:**

  TheSI TAM Teamis looking for **Data Optimization Analyst.** In this role you will be responsible for analyzing business KPIs combined with data from different processes involved in integrations with hospitality services suppliers (chains, bedbanks, platforms, etc) with the aim of finding opportunities to optimize these connectivities from both technical and business point of views.

  Main functions for this role will be to work closely together with Technical Account Managers focusing on analysis and providing recommendations to influence the way how they optimize these connectivities. It will also provide a meaningful input to Product Management and Applied Science team to shape how critical initiatives are developed and delivered.

  The role combines strong technical background on data and analytics together with understanding of business implications, working on implementing new solutions/tools and collaborating as a stakeholder with IT, Product Management, Applied Science, Technical Account Managers and Commercial teams.

  This role is an amazing opportunity to quickly learn how Hotelbeds business work in all its layers and have high visibility and exposure within the Hotelbeds eco-system interacting with a vast pool of stakeholders including top management.

  **Main Responsibilities:**

  - Work on analysis to support the business data-driven decision making
  - Investigate, propose, and validate potential improvements or upgrades in the optimization of certain processes with suppliers
  - Analyze, design, develop and automate the generation of certain reports to understand supplier performance
  - Create customizable tools to improve efficiency of certain processes
  - Crossing large volumes of data from different data sources with the goal to extract conclusions/opportunities and be able to share/present them.
  - Development of ad-hoc scripts for hypothesis testing.

  **Qualifications / Skills:**

  - Technical background / degree - computer science, or related
  - Knowledge of python with at least 2y of experience
  - Strong analytical skills with a data driven mindset
  - Experience analyzing big data and extracting conclusions and actions from it
  - Knowledge about RESTful APIs.
  - Familiarity interpreting data/logs from XML/JSON/YAML formats and working with SQL databases
  - Experience interpreting metrics / KPIs, step back, connect the dots and proactively think on opportunities to improve
  - Strong ability to understand business plans (commercial area) and their technical implications
  - Good communication and interpersonal skills
  - Proactive attitude and social skills
  - Experience using Microsoft office suite (Word, Excel, PowerPoint, Outlook…)
  - English professional proficiency. Strong written and verbal communication skills, and the ability to convey complex technical situations/conclusions to end users of all technical abilities, together with excellent presentation skills.

  **Key Challenges**

  - Strong technical, logical, analytical, and problem-solving skills
  - Team player with an agile mind-set
  - Combine a tech and business view, in a good common sense
  - Manage priorities to perform highest impact actions first
  - Ability to multi-tasking, working under pressure and in highly changing environments

  You will have the opportunity to work for a company that is going through significant change in becoming the worlds leading travel services provider. We are looking for people that are ready to ride the wave in this exciting journey.

  As well as an attractive benefits package you will be able to work: 

  - Within an innovative, engaging and multicultural environment.
  - Have the opportunity to build strong and lasting business relationships and friendships from around the world.
  - Have the opportunity in developing your career locally or within one of our beautiful working locations across the globe. 

  Summary

  - **Location:** Spain - Mallorca
  - **Type:** Full times
